---
title: "Test Marginal Likelihood"
author: "Frank"
date: "October 16, 2015"
output: html_document
---
The file ``SidTestData.RData`` contains data for testing the marginal likelihood calculation for the SUR model from the ``zoofactr`` package:
```{r}
library(zoofactr)
load("~/factor-choice/SidTestData.RData")
```
Loading this file adds a dataframe called ``prmdf`` to the environment:
```{r}
head(prmdf)
```
This data will be used to fit a two-equation SUR: ``prmibm ~ prmsp500`` and ``prmford ~ prmsp500`` in which Ford and IBM returns are regressed on the S&P500 index plus a constant.

We specify the prior as follows:
```{r}
# Normal prior for regression coefficients
beta0_ <- c(0,1,0,1) #mean vector
B0v_ <- diag(c(0.0025, 0.045, 0.0025, 0.045)) #var-cov matrix

# Wishart prior for the precision matrix of errors (inverse of var-cov) 
rho0_ <- 8  # degrees of freedom
R0_ <- diag(c(8000, 8000)) # scale matrix
```
We now calculate the marginal likelihood of this model based on 10000 posterior draws after discarding a burn-in sample of 1000 draws:
```{r}
logML_SUR(Y = as.matrix(prmdf[,c("prmibm", "prmford")]), 
          X = cbind(rep(1, nrow(prmdf)), prmdf$prmsp500), 
          G0 = B0v_, g0 = beta0_, R0 = R0_, r0 = rho0_, 
          n_draws = 10000, burn_in = 1000)
```
When Sid ran this calculation independently, he got a result of 3715.552.


